---
title: ""
css: ["assets/cronologia.css", "assets/cronologia.min.css"]
# format:
#   html: 
#   page-layout: custom
    # grid:
    #   sidebar-width: 0px
    #   body-width: 1000px
    #   margin-width: 300px
    #   gutter-width: 1.5rem
---


```{r setup, include=FALSE, echo=FALSE, message=FALSE}
knitr::opts_chunk$set(echo = TRUE)
options(width = 9999)

source(here::here("assets/timeline.R"))
library(tidyverse)
library(googlesheets4)
gs4_deauth()
md2_milestones <- read_sheet("https://docs.google.com/spreadsheets/d/1o1Bux8H0Xy-qqpApkalYfIOrhD8YbSWyf1S97yymMxw/") |> 
  rename(summary = Heading, description = Description) |> 
  mutate(Phase = str_to_title(Phase)) |> 
  fill(Phase)
phases <- unique(md2_milestones$Phase)
```

# ManyDogs 2: Overimitation

Our ManyDogs 2 project will be on overimitation in dogs. Overimitation occurs when an individual imitates another's action that is unnecessary to achieve a goal. For example, if you see someone wipe their brow before picking up a heavy object, wiping the brow isn't necessary to pick up the object. So copying the brow wiping would be an example of overimitation. Human children do this **a lot** ([Hoehl et al., 2019](https://doi.org/10.1016/j.dr.2018.12.002)), and dogs overimitate in certain situations ([Huber et al. 2020](https://doi.org/10.3758/s13420-019-00400-w)).

<center>
![Dog illustrating overimitation by touching a dot, which is irrelevant to the task. Source: [Huber et al., 2022](https://doi.org/10.3390/ani12030326)](images/dog_overimitation.png){fig-alt="Brown dog illustrating overimitation by nosing a blue dot on a wall." width=600}
</center>

In ManyDogs 2, we plan to leverage the power of large sample sizes across many labs to study overimitation in dogs. Completing the project is a long process, so we have outlined our project milestones below, letting you know where we are in the process. Keep checking it to see how we're coming along!

:::{.column-page}

## Project Milestones

### `r phases[1]`

```{r echo=FALSE, message=FALSE}
md2_project_development <- md2_milestones |> 
  filter(Phase == phases[1])
create_tml_split(df = md2_project_development, # the data frame
           smr = "summary", # the column that will be used in the summary 
           dsc = "description", # the column that will be used in the description
           split = 6
           )
```


### `r phases[2]`

```{r echo=FALSE, message=FALSE}
md2_data_collection <- md2_milestones |> 
  filter(Phase == phases[2])
create_tml_split(df = md2_data_collection, # the data frame
           smr = "summary", # the column that will be used in the summary 
           dsc = "description", # the column that will be used in the description
           split = 1
           )
```


### `r phases[3]`

```{r echo=FALSE, message=FALSE}
md2_data_processing <- md2_milestones |> 
  filter(Phase == phases[3])
create_tml_split(df = md2_data_processing, # the data frame
           smr = "summary", # the column that will be used in the summary 
           dsc = "description", # the column that will be used in the description
           split = 1
           )
```

:::

